---
title: "FaultTree package tutorial"
author: David J. Silkworth
site: bookdown::bookdown_site
output:
  bookdown::gitbook: default
documentclass: book
description: "Tutorial for the FaultTree package from openreliability.org"
---


# Prerequisites
Bookdown editing: [CarlesCG](https://github.com/CarlesCG)  
url: http://www.openreliability.org/fault-tree-analysis-on-r/  

This is a _sample_ book  written in **Markdown**. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.

For now, you have to install the development versions of **bookdown** from Github:

```{r eval=FALSE}
devtools::install_github("rstudio/bookdown")
```

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need to install XeLaTeX.

```{r include=TRUE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```
